% Parameters for init
\renewcommand{\arraystretch}{1.2}
\begin{longtable}[l]{| l || p{114mm} |}
\captionsetup{labelfont=bf}
\caption[\code{init} parameters]{\code{init} parameters. Your parameter file should have the following parameters.\\ \textcolor{myred}{\textbf{*}} indicates the required parameters, the other parameters are optional.}\\

\hline

-- \code{subTomoMeta}\textcolor{myred}{\textbf{*}} & Project name. Most output files will have the project name as prefix and the metadata is saved in a {\MATLAB} file called \code{<subTomoMeta>.mat}.\\ \hline

-- \code{Tmp\_samplingRate}\textcolor{myred}{\textbf{*}} & Sampling (i.e. binning) at which the template matching was ran. It should corresponds to the binning registered in the filename of the .csv and .mod file.\\ \hline

-- \code{fscGoldSplitOnTomos}\textcolor{myred}{\textbf{*}} & Whether or not the particles from the same subregions should be kept in the same half-set or distributed randomly. We do recommend to keep the sub-regions from overlapping and keep this parameter to 0/False. However, with tightly packed particles, which share a lot of their densities with other particles, it is better to set this parameter to 1/True to make sure the half sets don't share the same voxels.\\ \hline

-- \code{lowResCut} & This correspond to a rough estimate of the initial resolution of the data-set, directly coming out from the picking. The default value is set to 40\r{A} and it can be lowered for data-sets collected at low defocus. In most situation, the default value is fine to start with. As the processing goes, {\emClarity} will progressively lower this resolution estimate using the FSC.\\ \hline

\end{longtable}
