\section{Subtomogram averaging} \label{sec:avg}

\subsection{Objectives}

Once the tomograms are generated, {\emClarity} can calculate the subtomogram averages, one for each half-set. A volume-normalized single-particle Wiener (SPW) filter \cite{volume_normalized_SPW} will minimize the reconstruction error of the particle density by applying an ``optimal'' (low-pass) filter and correcting for all of the systematic changes to the signal imposed by the microscope and image processing algorithms on the reconstructions.

\begin{note}This filter is optimum as long as we correctly estimate the Signal-to-Noise Ratio of the two subtomogram averages (one for each half-set). This estimate depends on the conical Fourier shell correlation described in \myref{sec:algo:avg}.
\end{note}

\subsection{Parameters}

\input{Figures_Tables/11_parameters}

\subsection{Run}

To call the subtomogram averaging procedure:
\begin{lstlisting}
>> emClarity avg <param.m> <cycle_nb> RawAlignment
\end{lstlisting}

where \code{<param.m>} is the parameter file you want to use for this cycle, \code{<cycle\_nb>} is the cycle number, starting from 0. Each cycle starts with this step and is usually followed by the subtomogram alignment procedure. \code{RawAlignment} indicates to {\emClarity} that we want to calculate the subtomogram average of the entire half-set. As we'll see later, it is also possible to compute one average (one cluster) for each class.

If you suspect some densities are being omitted by the molecular mask or if you see extra `dust' outside your particle, you can change with the \code{shape\_mask\_*} parameters. If you want to only calculate the mask, you can run the following, with \code{shape\_mask\_test=1}:
\begin{lstlisting}
>> emClarity fsc <param.m> <cycle_nb> RawAlignment
\end{lstlisting}
The same molecular mask is used for averaging and alignment. The values that you use for the averaging will be used during the alignment.

\newpage
\subsection{Outputs}

The two subtomogram averages (half-maps) are saved into the project directory, as:\\ \code{cycleXXX\_projectName\_class0\_REF\_EVE.mrc}, and\\ \code{cycleXXX\_projectName\_class0\_REF\_ODD.mrc}.

The FSC is saved in \code{FSC/cycleXXX\_projectName\_Raw-1-fsc\_GLD.pdf}. The corresponding \code{.txt} file constains the FSC values. The first column is the resolution, in \r{A}\textsuperscript{-1}. The second column contains the Correlation Coefficients (CCs). The other 36 columns contain the CCs for each FSC cones.

For more details about the outputs, see \ref{sec:algo:avg}.